Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
edit

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode v_{\mathrm{rot}}\else $v_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode v_{\mathrm{out}}\else $v_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{\ifmmode \tau_{\mathrm{H}}\else $\tau_{\mathrm{H}}$~\fi}
\newcommand{\vth}{\ifmmode v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{./figures/results/doppler_shift_logtau6_theta90}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed perpendicular to the rotation axis}. 
    Here we fix $\tauh=10^6$ and $\theta=90^\circ$.
    We vary \vrot increasing from left to right and \vout increasing
    from top to bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifyin the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of
    only outflows, but also a Doppler shift from the rotational
    velocity (thick and dark line).  
    \label{fig:doppler_shift}}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{./figures/results/doppler_shift_logtau6_theta0}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed parallel to the rotation axis}.     
    Same layout as Figure \ref{fig:doppler_shift},
    this time the viewing angle corresponds to $\theta=0^\circ$.
    The effects of rotation on
    the  \lya\ line morphology are not visible when viewed parallel to
    the rotation axis.
    \label{fig:doppler_shift_theta_0}}
\end{figure}

@@

In Fig. \ref{fig:doppler} we present the spectrum of a LAE taken from to different
sides of the galaxy. As the LAE is rotating, one side is being redshifted while
the other is blueshifted. We see that the combined spectrum is a weighted line,
in solid black, that combines these past two. This shows that there is in fact a
Doppler Shift and then it justifies our choice to apply it after the outflows spectrum is
obtained.

@@

We find three different approaches how this model can have observational
implications. Firstly, as the resolution of astronomical instruments is
increasing, new images from LAEs can be spatially resolved in a way that
rotation velocities of the galaxy can be determined. New spectrographs like
MUSE should help obtain kinematic information from LAEs by using our model.
As for now, previous works in the literatures have already found useful data
to support this idea. Fig 7 of Prescott et al. \cite{Prescott14} shows the
presence of Doppler shift and \cite{Herenz2016} creates 2D line of sight
velocity maps of several LARS (Lyman Alpha Reference Sample) galaxies.

\color{red}
Kulas...
\color{black}
Finally, we present a reconstruction of a selected \lya spectrum presented
by \cite{Kulas12} and reproduced with the permission of the author. We create
a fit of the \lya line and predict its kinematic properties.

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{float}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}
\usepackage{dblfloatfix}
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode v_{\mathrm{rot}}\else $v_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode v_{\mathrm{out}}\else $v_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{\ifmmode \tau_{\mathrm{H}}\else $\tau_{\mathrm{H}}$~\fi}
\newcommand{\vth}{\ifmmode v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

\begin{figure*}
\centering
    \includegraphics[width=0.48\textwidth]{./figures/results/doppler_shift_logtau6_theta90}
    \includegraphics[width=0.48\textwidth]{./figures/results/doppler_shift_logtau6_theta0}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity viewed perpendicular/paralell to the
      rotation axis}.  
    Here we fix $\tauh=10^6$. 
    The six panels on the left correspond to $\theta=90^\circ$ and the
    panels on the right to $\theta=0^{\circ}$
    We vary \vrot increasing from left to right and \vout increasing
    from top to bottom. 
    The thin black line corresponds to the \lya line obtained with
    CLARA without any rotation and the indicated outflow velocity.
    The thick black line corresponds to the results including both
    outflows and rotation.
    The thick gray line shows the results of modifyin the pure outflow
    solution by the Doppler shift presented in Equation \ref{eq:shift_x}
    (in thin line), if there is a radiative transfer of rotation and outflows
    (thick and clear line), and if there is a radiative transfer of
    only outflows, but also a Doppler shift from the rotational
    velocity (thick and dark line).  
    \label{fig:doppler_shift}}
\end{figure*}

@@

\subsection{Links to observations}

There are at least three inmmediate ways the work we have presented
here can be useful to observational efforts.

\subsubsection{Kinematic Maps}
The first is related to the capability of spatially resolving the
extent of a LAE.
For instance \cite{Prescott14} presented observational results of a
Doppler shift when taking spectra at two oposite sides of a LAE.

In Figure \ref{fig:doppler} we present a toy model for the spectrum of
a LAE taken from to different sides of the galaxy. 
As the LAE is rotating, one side is being redshifted while the other
is blueshifted. 
We see that the full spectrum is a weighted line, in solid black,
that is found between these two.
In this toy model the rotational velocity is \vrot$=100\ \kms$. 
We highlight that the distance between the maxima of the blue and red
spectra is not twice the rotational velocity as it could be naively
expected.
Although the spectra can be modeled by Doppler shifts, the peak of the
spectra is also weighted by the amount of mass that has a given
velocity. 
In this toy model

New spectrographs like MUSE should help obtain kinematic information
from LAEs to build velocity maps in \lya. 
This could be a natural extension of the work reported by
\cite{Herenz2016} on the velocity maps of several LARS (Lyman Alpha
Reference Sample) galaxies.

@@

We find three different approaches how this model can have observational
implications. Firstly,
